### 2014-10-09 writing/AAAI SSS '15/wordnet.tex
Incomplete results update

\paragraph{Results} 
We find that with only a small amount of hyperparamater tuning, our model can perform almost perfectly, and that performance remains fairly good even when the fraction of the training data used is decreased.

@@

\begin{table}[h]
\centering\resizebox{4in}{!}{\small
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{l c l l} 
    \toprule
    Comparison layer & \% training data & w/ GloVe & w/o GloVe \\
    Most frequent class & -- & 37.9 (--) & 37.9 (--) \\
    NN       & 100\%   & TODO & TODO \\
    NN       & 75\%   & 98.6 (100.0) & TODO \\
    NN       & 33\%   & TODO & 37.0 (37.0) \\ % TODO: See if this improves
    NN       & 16\%   & TODO & 92.0 (100.0)\\
    NTN       & 100\%   & 99.6 (100.0) & 99.4 (99.9) \\
    NTN       & 75\%   & 98.6 (100.0) & TODO\\
    NTN       & 33\%   & 95.1 (99.8) & 95.2 (100.0) \\
    NTN       & 16\%   & 94.6 (100.0) & 92.1 (100.0) \\
    \bottomrule
  \end{tabular}}
 \caption{Test (train) accuracy figures on the WordNet data.\label{b-table}}  
\end{table}

>>>>

\paragraph{Results} 
We find that with only a small amount of hyperparamater tuning, our model can perform almost perfectly, and that performance remains fairly good even when the fraction of the training data used is decreased. Neither model has reached perfect performance in any of our experiments, though we are 
continuing to tune both models. We find that the NN and NTN both capture the required
generalizations extremely well.

@@

\begin{table}[h]
\centering\resizebox{4in}{!}{\small
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{l c l l l l} 
    \toprule
    Comparison layer & \% training data & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} \\
     &  & NN & NTN & NN & NTN \\
    \midrule
    Baseline & -- & 37.9 (--) & 37.9 (--) & 37.9 (--) & 37.9 (--) \\
    \midrule
    NN       & 100\%   & 99.5 (100.0) & 98.9 (99.7) \\
    NN       & 75\%   & 98.9 (100.0) & 37.9 (37.0) \\
    NN       & 33\%   & 96.0 (100.0) & 37.0 (37.0) \\ % TODO: Rerunning. Got stuck predicting the most frequent class.
    NN       & 16\%   & 91.8 (100.0) & 91.9 (100.0)\\
    \midrule
    NTN       & 100\%   & \textbf{99.6} (100.0) & 99.2 (100.0) \\
    NTN       & 75\%   & 98.6 (100.0) & 98.4 (100.0)\\
    NTN       & 33\%   & 95.4 (100.0) & 95.3 (100.0) \\
    NTN       & 16\%   & 92.1 (99.7) & 92.2 (100.0) \\
    \bottomrule
  \end{tabular}}
 \caption{Test (train) accuracy figures on the WordNet data. The baseline figure is simply the frequency of the most frequent class, \ii{coordinate}.\label{b-table}}  
\end{table}
